R für die sozio-ökonomische Forschung

### 2019-11-18 figures/A-Markdown-Ordnerstruktur.tex

\begin{forest}
  pic dir tree,
  pic root,
  for tree={
    directory,
  }, % START SPECIFYING DIR TREE
[MarkdownProject
  [data
  [BIP-Data.csv, file]],
  [R
  [R-Skript.R, file], 
  [OurMarkdown.Rmd, file]
  ]
  [Output]
]
\end{forest}

>>>>

\begin{forest}
  pic dir tree,
  pic root,
  for tree={
    directory,
  }, % START SPECIFYING DIR TREE
[MarkdownProject
  data,
  [BIP-Data.csv, file]],
  [R
  [R-Skript.R, file], 
  [OurMarkdown.Rmd, file]
  ]
  [Output]
]
\end{forest}
